HO unification from object language to meta language

### 2024-03-18 paper/main.tex
review mode
latex

\documentclass[sigconf,natbib=false]{acmart}
\usepackage[]{biblatex}

@@

In order to reason about unification we provide a description of the
\Fo{} and \Ho languages where unification variables
are first class terms, i.e. they have a concrete syntax. We keep these languages
minimal, for example we omit the \elpiIn{all} quantifier of DTT we used
in the example in Section~\ref{sec:intro}. 
%
\setlength{\abovecaptionskip}{0pt}
\setlength{\belowcaptionskip}{-13pt}

@@

\noindent
In the case of \Fo{} unification variables \elpiIn{fuva} have no explicit scope:
Unification variables standing for functions are applied their arguments
via the \elpiIn{fapp} constructor.
For example in the statement of the instance \coqIn{forall_dec} the
term \coqIn{P x} is represented as \elpiIn{fapp[fuva N, x]}, where \elpiIn{N}
is of type \elpiIn{nat} and \elpiIn{x} is a bound variable.

@@

\noindent
The \elpiIn{name} builtin predicate tests if a term is a bound variable.
\footnote{one could always load name x for every x under a pi and get rid of the name builtin}
The
compiler~\ref{sec:xxx} needs to support terms outside \llambda for practical
reasons, so we don't assume all out terms are in \llambda but rather test.

@@

>>>>

\documentclass[sigconf,natbib=false,review]{acmart}
\usepackage[]{biblatex}

@@

In order to reason about unification we provide a description of the
\Fo{} and \Ho languages where unification variables
are first class terms, i.e. they have a concrete syntax. We keep these languages
minimal, for example, we omit the \elpiIn{all} quantifier of DTT we used
in the example in Section~\ref{sec:intro} together with the type notation of
terms carried by the \elpiIn{lam} constructor. 
%
\setlength{\abovecaptionskip}{0pt}
\setlength{\belowcaptionskip}{-13pt}

@@

\noindent
In the case of \Fo{} unification variables \elpiIn{fuva} have no explicit scope:
the arguments of an higher order unification variable are via the \elpiIn{fapp}
constructor. For example in the statement of the instance \coqIn{forall_dec} the
term \coqIn{P x} is represented as \elpiIn{fapp[fuva N, x]}, where \elpiIn{N} is
a memory address and \elpiIn{x} is a bound variable.

@@

\noindent
The \elpiIn{name} builtin predicate tests if a term is a bound variable.
\footnote{one could always load name x for every x under a pi and get rid of the name builtin}
The
compiler~\ref{sec:xxx} needs to support terms outside \llambda for practical
reasons, so we don't assume all out terms are in \llambda but rather test. \textbf{\textcolor{red}{what?? }}

@@

TODO: invariant: variables in subst are always fully applied, and length of scope is the
arity of the HO variable.
